---
title: "2021 1-Year Estimate 65+ ALL STATES"
author: "Anish Mangipudi"
format: html
editor: visual
---

```{r}
#| warning: false
#| message: false

library(tidycensus)
library(tidyverse)
library(choroplethr)
library(choroplethrMaps)
library(scales)
library(plotly)

df = get_acs(geography = "State",
             variables = c(pop_65_plus = "S0101_C01_030"),
             survey    = "acs1",
             year      = 2021,
             output    = "wide",
             cache_table = TRUE)
total_df = get_acs(geography = "State",
             variables = c(total = "S0101_C01_001"),
             survey    = "acs1",
             year      = 2021,
              output    = "wide",
              cache_table = TRUE)
percent_df  = get_acs(geography = "State",
                     variables = c(total = "S0101_C01_001"),
                     survey    = "acs1",
                     year      = 2021,
                     output    = "wide",
                     cache_table = TRUE)

names(df) <-c("geoid" ,"region" ,"value", "moe")
names(total_df) <-c("geoid" ,"region" ,"value", "moe")
names(percent_df) <-c("geoid" ,"region" ,"value", "moe")

df$region = tolower(df$region)
percent_df$region = tolower(percent_df$region)
total_df$region = tolower(total_df$region)

percent_df$value = ((df$value/total_df$value) * 100)
total_df$value = total_df$value - df$value

state_choropleth(percent_df,
                 title = "PERCENT POPULATION OVER 65 \n2021 1-YEAR ACS S0101_C01_001",
                 legend = "PERCENTAGE",
                 num_colors = 4
                 )

x = ggplot(percent_df, aes(y = value)) +
  geom_boxplot(color="red", fill="orange", alpha=1) + 
  scale_y_continuous(label=comma) +
  ggtitle("PERCENT DISTRIBUTION STATES\n WITH POPULATION 65+") +
  xlab("")+
ylab("POPULATION")+
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) 
ggplotly(x)
```

This is the main distribution of Data, the median is 17.39 percent

1st Quartile - 16.42%

3rd Quartile - 18.43%

Max 22.69% in Puerto Rico

Min 11.63% in Utah

Also included is a Choroplethr to better Visualize the data

## MAP AGE 65+

## CODE

```{r}
#| warning: false
#| message: false

df = get_acs(geography = "State",
             variables = c(pop_65_plus = "S0101_C01_030"),
             survey    = "acs1",
             year      = 2021,
             output    = "wide",
             cache_table = TRUE)
df$NAME = tolower(df$NAME)
names(df) <-c("geoid" ,"region" ,"value", "moe")

state_choropleth(df, 
                 title         = "POPULATION 65+ \n2021 1-YEAR ACS S0101_C01_030",
                 legend        = "POPULATION",
                 num_colors = 4)

x = ggplot(df, aes(y = value)) +
  geom_boxplot(color="red", fill="orange", alpha=1) + 
  scale_y_continuous(label=comma) +
  ggtitle("POPULATION DISTRIBUTION STATES\n WITH POPULATION 65+") +
  xlab("")+
ylab("POPULATION")+
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
ggplotly(x)
```

Here is the actual number of individuals age 65 or above as represented in this boxplot distribution. Median is 767,373.

1st Quartile - 318,421.5

3nd Quartile - 1,292,812.5

Min - 85,615 in DC

Max - 5,964,526 in California

Choroplethr also included to better visualize data.
